\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvstyle{banking}
\moderncvcolor{black}
\nopagenumbers{}
\usepackage[utf8]{inputenc}
\usepackage{ragged2e}
\usepackage[scale=0.915]{geometry}
\usepackage{import}
\usepackage{multicol}
\usepackage{import}
\usepackage{enumitem}
\usepackage[utf8]{inputenc}
\usepackage{amssymb}
\name{Vighnesh}{Sivaraman}
\newcommand*{\customcventry}[7][.13em]{
\begin{tabular}{@{}l}
{\bfseries #4} \
{\itshape #3}
\end{tabular}
\hfill
\begin{tabular}{l@{}}
{\bfseries #5} \
{\itshape #2}
\end{tabular}
\ifx&#7&%
\else{\
\begin{minipage}{\maincolumnwidth}%
\small#7%
\end{minipage}}\fi%
\par\addvspace{#1}}
\begin{document}
\makecvtitle
\vspace*{-16mm}
\begin{center}\textbf{ Software Engineer/Machine Learning Engineer}\end{center}
\begin{center}
\begin{tabular}{ c c c }
\faMobile\enspace +91 8148285956 & \enspace vighneshsivaraman@gmail.com & \faHome\enspace Chennai,TN,IND \\
\faLinkedin\enspace \color{blue} \href{https://www.linkedin.com/in/vighnesh-sivaraman/}{in/vighnesh-sivaraman} &
\faGithub\enspace \color{blue} \href{https://github.com/VighneshS}{github.com/VighneshS} & \enspace {$\mathbb{X}$}\enspace \color{blue} \href{https://x.com/jeevavighnesh}{x.com/jeevavighnesh}
\end{tabular}
\end{center}

\section{Profile}
{Experienced Software Engineer with over 4 years of expertise in \textbf{DevOps} and \textbf{full stack engineering}, currently pivoting towards \textbf{Data Science} and \textbf{Machine Learning}. Successfully contributed to projects at Revature LLC, demonstrating strong technical skills in the development and integration of complex microservice web applications. Recently completed a Master’s degree in Computer Science from a U.S. university, where I interned at a startup, honing my ML skills. Passionate about leveraging machine learning to solve real-world problems and drive innovation. Proficient in various programming languages and technologies, and eager to apply my knowledge in a dynamic and challenging environment to gain extensive experience.}

\section{Areas of Expertise}
{Data Analysis - Data Visualization - Image Segmentation - Natural Language Processing - RNN Models - GAN Models - Deep Learning Models - Distributed Systems - Multi-Threading - Microservices Development - Spring Framework - Angular - Database Management Systems - Cloud Services (AWS and GCP)}

\section{Professional Experience}
\customcventry{01/2023 ‐ 07/2024}{{\color{blue}\href{https://www.aliciotech.com/}{Allic Infotech}}}{Machine Learning Engineer Intern,}{Silicon Valley, CA}{}{
{\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
\item Developed a Python-based application for detecting individual layers of human skin from ultrasound images using an RNN model.
\item Established pipelines to deploy the application as a web app.
\end{itemize}}}

\customcventry{09/2022 ‐ 01/2023}{{\color{blue}\href{https://revature.com/}{Revature, LLC}}}{Data Analyst Intern,}{Reston, VA}{}{
{\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
\item Created notebooks for ensuring data warehouse integrity in Azure Databricks.
\item Developed visual reports using Power BI and gained knowledge in data warehousing ETL pipeline concepts.
\end{itemize}}}

\customcventry{02/2022 ‐ 09/2022}{{\color{blue}\href{https://ranger.uta.edu/~mingli/}{The University of Texas at Arlington}}}{Graduate Research Assistant,}{Arlington, TX}{}{
{\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
\item Developed Android applications and machine learning models for various research papers including "Continuous Authentication using Human-Induced Electric Potential".
\item Organized workshops and contributed to the creation of a cloud-based IoT system for water quality monitoring.
\end{itemize}}}

\customcventry{08/2016 ‐ 12/2020}{{\color{blue}\href{https://revature.com/}{Revature, LLC}}}{Senior Software Engineer,}{Chennai, TN, IND}{}{
{\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
\item Led a team of five members for the Operations and Management team, overseeing daily production bug fixes and feature improvements.
\item Developed microservices for web applications using MySQL, Java Spring framework, and Angular.
\item Managed and improved product infrastructure on AWS and GCP, including EC2, RDS, EKS, and Terraform scripts.
\end{itemize}}}

\iffalse
\section{Online Courses \& Certifications}
{\begin{itemize}[label=\textbullet]
      \item Introduction to Digital Marketing (Jan. 2023) - \underline{\color{blue}\href{https://google.com/}{SEMRUSH}}
      \item Career Essentials in Digital Marketing by LinkedIn (Aug. 2022) - \underline{\color{blue}\href{https://google.com/}{LinkedIn}}
      \item Visualization with Tableau (Feb. 2022) - \underline{\color{blue}\href{https://google.com/}{Coursera}}
      \item Foundations of Google Analytics  (Jun. 2021) - \underline{\color{blue}\href{https://google.com/}{Google, Coursera}}
     \item Google Analytics for Power Users (Jun. 2021) - \underline{\color{blue}\href{https://google.com/}{Google}}
       \item The Fundamentals of Digital Marketing, (Jul. 2019) - \underline{\color{blue}\href{https://google.com/}{Google}} 
  \end{itemize}} 
\fi

\section{Education}
\customcventry{2021-2023}{\color{blue}\href{https://www.uta.edu/}{The University of Texas at Arlington}}{MS Computer Science (Thesis)}{Arlington, TX, USA}{}{}{Relevant Courses: Data Mining, Artificial Intelligence, Machine Learning, Web Data Management, Design and Analysis of Algorithms, Neural Networks, and Information Security.}

\section{Projects}
\customcventry{Tools: Python 3.7, Twitter API V2.2, NLTK}{\color{blue}\href{https://vighnesh-studies.blogspot.com/2021/05/disaster-alert-system.html}{Disaster Alert System}}{Data Mining}{}{}{}{Developed by analyzing tweets by categorizing a tweet as a disaster or not by using the Naive Bayes Classifier and improving it's performance using K-fold cross-validation.}

\customcventry{Tools: Python 3.7, SCIKIT-LEARN, Tensorflow 2.7, Keras}{\color{blue}\href{https://github.com/VighneshS/neura_colorizer}{Neura Coloriser}}{Machine Learning}{}{}{}{Created a Neura Coloriser, a Generative Adversarial Network to paint colours to an input grey-scale image. Used LAB colour space representations and a self-developed GAN for generating the colour images.}

\customcventry{Tools: Python 3.7, PriorityQueue}{\color{blue}\href{https://github.com/VighneshS/find_route}{find\_route}}{Artificial Intelligence}{}{}{}{Implement 'find\_route' an application which uses A* Search Algorithm to find the route from a start state to goal state using Priority Queues and has 2 modes of operations to perform an informed search using a known heuristic and uninformed search.}

\customcventry{Tools: HTML, CSS and JavaScript.}{\color{blue}\href{https://github.com/VighneshS/sorting-visualization}{Sorting Visualization}}{Design and Analysis of Algorithms}{}{}{}{Designed Web application for Sorting to visualize and analyze different sorting algorithms including Heap, Quick, 3 Median Quick-sort, Insertion, Bubble and Selection, to compare their time complexities and total iterations taken.}

\customcventry{Tools: React v18, MySQL 5.6, PHP 8.0, Laravel, NodeJS 17.9}{\color{blue}\href{https://github.com/VighneshS/siremar}{Siremar}}{Web Data Management}{}{}{}{Created a web Application that uses all CRUD operations with chat functions using WebSockets and Visual charts for analyzing each user.}

\customcventry{Tools: C++}{\color{blue}\href{https://github.com/VighneshS/keylogger}{KeyLogger}}{Information Security}{}{}{}{Redesigned KeyLogger application to automatically install windows service which logs the keystrokes of the computer. Uses keyboard hook handles to register keystrokes and a registry to hide itself from plain sight to run as a service in the background.}

\section{Publications}
\customcventry{}{}{\color{blue}\href{https://doi.org/10.1145/3627106.3627124}{Continuous Authentication Using Human-Induced Electric Potential}}{}{}{}{Murali, S., Jin, W., Sivaraman, V., Zhu, H., Ji, T., Li, P., \& Li, M. (2023). In Proceedings of the 39th Annual Computer Security Applications Conference (ACSAC 2023). Association for Computing Machinery. DOI: 10.1145/3627106.3627124}

\customcventry{}{}{\color{blue}\href{https://www.academia.edu/38392049/Real_TimeAccident_Analytics}{Real-time accident analytics}}{}{}{}{Published at Journal of Chemical and Pharmaceutical Sciences, ISSN: 0974-2115 on June 2017}

\section{Skills}
{\begin{itemize}[label=\textbullet]
\item {\textbf{Data Science \& Machine Learning:} TensorFlow, PyTorch, Scikit-learn, Data Analysis \& Visualization}
\item {\textbf{Database Management:} MySQL, Databricks}
\item {\textbf{Programming Languages:} Java, Python, JavaScript, C++, Node.js}
\item {\textbf{Web Development:} HTML, CSS, JavaScript, Angular}
\item {\textbf{Cloud Platforms:} AWS (EC2, RDS, EKS, Lambda, CloudwatchLogs, ECR, Route53), GCP, Azure}
\item {\textbf{DevOps Tools:} Jenkins, Terraform, Docker, Kubernetes}
\item {\textbf{Software Development:} Microservices, Android Development, iOS Development}
\item {\textbf{Data Visualization:} Power BI, matplotlib, RStudio}
\end{itemize}}

\iffalse
\section{Languages}
\begin{multicols}{2}
    \begin{itemize}[label=\textbullet]
    \item \textbf{English} [Native]
    \item {\textbf{French} [Basic] - Learning}
    \item {\textbf{Spanish} [Native]}
    \item {\textbf{German} [Basic] - A1}
    \end{itemize}
\end{multicols}
\fi
\end{document}